---
title: "Final Project"
author: "Soobin Choi"
date: "2022-10-01"
output: 
  github_document: 
    toc: TRUE
---

# Developmental process of L2 - English and Korean

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo=TRUE, include=TRUE, comment="")
library(tidyverse)
library(tidytext)
library(repurrrsive)
library(quanteda)
library(magrittr)

```


## Korean Learners' Corpus (KLC)

### Data Import


```{r}
KLC <- read_tsv(file = "https://github.com/jungyeul/korean-learner-corpus/raw/main/data/kyunghee_v2.tsv", locale(encoding = "UTF-8")) 
```


### Data Manipulation


```{r}
# change column names with clearer description
KLC <- KLC %>% 
  rename(ID = X1,
         Nationality = X2,
         Gender = X3,
         Topic = X4,
         Text = X5,
         Morphemes = X6,
         Level = X7,
         Score = X8)

# remove some values with error
KLC_clean <- KLC %>% 
  filter(Level %in% c("A1", "A2", "B1", "B2", "C1", "C2"))

```



```{r}

# filter the data with nationality.
KLC_eng <- KLC_clean %>% 
  filter(Nationality %in% c("미국", "영국", "호주", "필리핀", "싱가포르", "인도", "르완다"))

```

When filtering nationality of participants, I was not sure what sort of criterium I should apply. I know a huge part of the population in Thailand speaks English, then should I include them too?

So, I ended up sorting out the countries whose official language includes English.
It would have been easier for me to sort out if there is a column about their first language, not their nationality.

### Tokenization

```{r}
KLC_tok <- KLC_eng %>% 
  select(ID, Nationality, Text) %>% 
  unnest_tokens(word, Text)

KLC_eng %>% 
  select(ID, Nationality, Text) %>% 
  unnest_tokens(word, Text) %>% 
  group_by(ID)
```

#### 1. Lexical Diversity

how to calculate lexical diversity: how many different words are used in each person's essay?; the number of _word type_ divided by the number of _tokens_ / TTR

```{r}

## making a clean version of the data; 

KLC_clean <- KLC_eng %>%
  select(ID, Morphemes) %>% 
  map(~ str_split(., " (\\+)?")) %>% 
  as_data_frame() %>% 
  rename(num_token = Morphemes) %>% 
  unnest(ID) %>% 
  left_join(KLC_eng, .,  by="ID") %>% 
  relocate(num_token, .after = ID) %>% 
  select(-c(Gender, Topic))


# word type and wort token, TTR

KLC_numtok <- KLC_clean %>% 
  unnest(num_token) %>% 
  group_by(ID) %>% 
  count(ID, name = "num_token")

KLC_numdist <- KLC_clean %>% 
  unnest(num_token) %>% 
  group_by(ID) %>% 
  summarize(num_dist = n_distinct(num_token))

###### n_distinct = unique(length())


KLC_a <- left_join(KLC_numdist, KLC_numtok, by = "ID") %>% 
  mutate(TTR = (num_dist / num_token))

min(KLC_lex_div$num_token)
max(KLC_lex_div$num_token)

###### essay별 TTR

KLC_TTR <- left_join(KLC_a, KLC_clean %>% select(ID, Level), KLC_a, by = "ID") %>% 
  group_by(Level) %>% 
  summarize(TTR = mean(TTR), mean_text_len = mean(num_token))


```



#### 2. Syntactic Complexity

how to calculate syntactic complexity: compare average sentence length  


```{r, error=TRUE}

KLC_sent <- KLC_clean %>% 
  unnest_tokens(Sentence, Text, "sentences") 




KLC_morph <- KLC_sent %>% 
  unnest(num_token) %>% 
  mutate(sent_num = lag(num_token) %>% 
           str_detect("/EF$") %>% 
           replace_na(FALSE) %>% 
           cumsum() %>% 
           add(1),
         .after = num_token)
##### sentence length

KLC_syncom <- KLC_morph %>% 
  select(-Nationality, -Morphemes, -Score, -Sentence) %>% 
  group_by(sent_num) %>% 
  mutate(sent_len = length(ID)) %>% 
  group_by(Level) %>% 
  summarize(mean_sent_len = mean(sent_len))

##### above is what I need

  
# count하고나서 num_token을 살리고 싶으면 어떻게해야하지?
# summarize 대신 mutate!



'''
count: 데이터프레임
length: 벡터값
'''
```


## KLC final

```{r}
KLC_TTR
KLC_syncom
```



```{r}
# Lag & lead?
KLC_clean %>% 
  head() %>% 
  mutate(ID_lag = lag(ID),
         ID_lead = lead(ID))
```


## PELIC


### Data Import


```{r}
PELIC_ans <- read_csv("https://github.com/ELI-Data-Mining-Group/PELIC-dataset/raw/master/corpus_files/answer.csv")

PELIC_crs <- read_csv("https://github.com/ELI-Data-Mining-Group/PELIC-dataset/raw/master/corpus_files/course.csv")

PELIC_id <- read_csv("https://github.com/ELI-Data-Mining-Group/PELIC-dataset/raw/master/corpus_files/student_information.csv")

PELIC_scr <- read_csv("https://github.com/ELI-Data-Mining-Group/PELIC-dataset/raw/master/corpus_files/test_scores.csv")

PELIC_ques <- read_csv("https://github.com/ELI-Data-Mining-Group/PELIC-dataset/raw/master/corpus_files/question.csv")
```

### Data manipulation

** sorting out columns needed
```{r}

PELIC_scr1 <- PELIC_scr %>% 
  select(anon_id, MTELP_Conv_Score, Writing_Sample)

PELIC_crs1 <- PELIC_crs %>% 
  select(course_id, level_id)

PELIC_ans1 <- PELIC_ans %>%
  select(anon_id, course_id, question_id, text_len, text, tokens, tok_lem_POS)
  
PELIC_id1 <- PELIC_id %>% 
  select(anon_id, native_language)

PELIC_ques1 <- PELIC_ques %>% 
  select(question_id, question_type_id)
```

* course_id: a unique identifier for each course - a 1-4 digit integer, e.g. 987

* level_id:	a code to identify in which of the four levels the text was produced (5 the highest)


```{r}
left_join(PELIC_ans1, PELIC_ques1, by = "question_id") %>% 
  relocate(question_type_id, .after = question_id) %>% 
  filter(question_type_id %in% c(4))

```




** Joining all the columns in one dataframe

```{r}
PELIC1 <- left_join(PELIC_ans1, PELIC_crs1, by = "course_id") %>%  
  relocate(c(level_id), .after = course_id)
PELIC2 <- left_join(PELIC1, PELIC_id1,by = "anon_id")
PELIC3 <- left_join(PELIC2, PELIC_scr1, by = "anon_id")

PELIC_clean <- PELIC3 %>% 
  filter(native_language == "Korean", text_len > 43, 475 > text_len) %>% 
  relocate(c(text, tokens),.after = Writing_Sample)

PELIC_clean <- PELIC_clean %>% 
  mutate(rownum = c(1:3549)) %>% 
  relocate(rownum, .after = anon_id)



```

#### 1. Lexical Diversity

how to calculate lexical diversity: how many different words are used in each person's essay?; the number of _word type_ divided by the number of _tokens_

```{r, error=TRUE}

# cleaning POS data

lemPOS <- PELIC_clean %>% 
  mutate(tok_lem_POS = tok_lem_POS %>% 
           str_remove_all("\\[\\(") %>% 
           str_remove_all("\\)\\]") %>% 
           str_remove_all("\\(") %>% 
           str_remove_all("'") %>% 
           str_split("\\),")) %>% 
  unnest(tok_lem_POS) %>% 
  separate(tok_lem_POS, into = c('token', 'lemma', 'POS'), sep = ',') %>% 
  select(-token) %>% 
  filter(!(lemma == "")) %>% 
  unite(lemPOS, lemma, POS, sep = ",")


mean_level <- PELIC_clean %>% 
  group_by(anon_id) %>% 
  summarize(mean_lev = round(mean(level_id)))

unique(PELIC_clean$level_id)

### FINAL!!!

PELIC_TTR <- left_join(lemPOS1, mean_level, by = "anon_id") %>% 
  select(-c(course_id:question_id), -c(native_language:tokens)) %>% 
  group_by(rownum) %>% 
  summarize(lemPOS_type = length(unique(lemPOS)),
            lemPOS_token = length(lemPOS)) %>% 
  left_join(., PELIC_clean %>% select(anon_id, rownum, level_id), by = "rownum") %>% 
  group_by(level_id) %>% 
  summarize(TTR = mean(lemPOS_type/lemPOS_token),
            mean_text_len = mean(lemPOS_token))

unique(PELIC_clean$level_id)

```



```{r}
### This is not needed for my final; just save for my future research

PELIC_clean %>% 
  unnest_tokens(sentence, text, token = "sentences") %>% 
  filter(anon_id == "ad1")

# calculate TTR per sent / per text

  # TTR per sent
  
sent_TTR <- lemPOS %>% 
  left_join(., mean_level, by = "anon_id") %>% 
  group_by(anon_id) %>% 
  mutate(sent_num = cumsum(str_detect(lemma, regex("\\."))) %>% add(1)) %>% 
  ungroup() %>% 
  group_by(anon_id, sent_num, mean_level) %>% 
  summarize(dist_morph = n_distinct(lemma),
            num_morph = n(),
            sent_TTR = dist_morph/num_morph)


```


#### 2. Syntactic Complexity

how to calculate syntactic complexity: Long, complex sentences vs. short. simple sentences

```{r, error=TRUE}

lemPOS1 <- PELIC_clean %>% 
  mutate(tok_lem_POS = tok_lem_POS %>% 
           str_remove_all("\\[\\(") %>% 
           str_remove_all("\\)\\]") %>% 
           str_remove_all("\\(") %>% 
           str_remove_all("'") %>% 
           str_split("\\),")) %>% 
  unnest(tok_lem_POS) %>% 
  separate(tok_lem_POS, into = c('token', 'lemma', 'POS'), sep = ',') %>% 
  select(-token) %>% 
  filter(!(lemma == ""))

PELIC_syncom <- lemPOS1 %>% 
  group_by(anon_id) %>% 
  mutate(sent_num = cumsum(str_detect(lemma, regex("\\."))) %>% add(1)) %>% 
  ungroup() %>% 
  select(-c(rownum:course_id), -question_id, -c(native_language:tokens)) %>% 
  unite(lemPOS, lemma, POS, sep = ",") %>% 
  group_by(anon_id, sent_num) %>% 
  mutate(sent_len = length(anon_id),
         mean_texlen = mean(text_len)) %>% 
  group_by(level_id) %>% 
  summarize(mean_sent_len = mean(sent_len))

unique(lemPOS1$level_id)
```


## sum-up

```{r}
PELIC_TTR
PELIC_syncom
```



# comparison between KLC and PELIC

```{r}
KLC_TTR
PELIC_TTR

KLC_syncom
PELIC_syncom
```

### Data Visualization

```{r}
KLC_TTR_vis <- KLC_TTR %>% 
  mutate_all(funs(str_replace_all(., c("A1" = "1",
                                     "A2" = "2",
                                     "B1" = "3",
                                     "B2" = "4",
                                     "C1" = "5",
                                     "C2" = "6")))) %>% 
  mutate(TTR = as.numeric(TTR)) %>% 
  mutate(mean_text_len = as.numeric(mean_text_len)) %>% 
  mutate(TTR = round(TTR, 4),
         mean_text_len = round(mean_text_len))

KLC_syncom_vis <- KLC_syncom %>% 
    mutate_all(funs(str_replace_all(., c("A1" = "1",
                                     "A2" = "2",
                                     "B1" = "3",
                                     "B2" = "4",
                                     "C1" = "5",
                                     "C2" = "6")))) %>% 
  mutate(mean_sent_len = as.numeric(mean_sent_len)) %>% 
  mutate(mean_sent_len = round(mean_sent_len))

```

```{r}


## KLC_TTR
left_join(KLC_a, KLC_clean %>% select(ID, Level), KLC_a, by = "ID") %>% 
  ggplot(aes(x = num_token, y = TTR, col = Level)) + 
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, col = "yellow") 

## KLC_syncom

KLC_morph %>% 
  select(-Nationality, -Morphemes, -Score, -Sentence) %>% 
  group_by(sent_num) %>% 
  mutate(sent_len = length(ID)) %>% 
  ggplot(aes(x = Level, y = sent_len, fill = Level)) + 
  geom_boxplot() 


## PELIC TTR


left_join(lemPOS1, mean_level, by = "anon_id") %>% 
  select(-c(course_id:question_id), -c(native_language:tokens)) %>% 
  group_by(rownum) %>% 
  summarize(lemPOS_type = length(unique(lemPOS)),
            lemPOS_token = length(lemPOS)) %>% 
  left_join(., PELIC_clean %>% select(anon_id, rownum, level_id), by = "rownum") %>% 
  ggplot(aes(x = num_token, y = TTR, col = Level)) + 
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, col = "yellow") 


## PELIC syncom

lemPOS1 %>% 
  group_by(anon_id) %>% 
  mutate(sent_num = cumsum(str_detect(lemma, regex("\\."))) %>% add(1)) %>% 
  ungroup() %>% 
  select(-c(rownum:course_id), -question_id, -c(native_language:tokens)) %>% 
  unite(lemPOS, lemma, POS, sep = ",") %>% 
  group_by(anon_id, sent_num) %>% 
  mutate(sent_len = length(anon_id),
         mean_texlen = mean(text_len)) %>% 
  mutate(level_id = as.character(level_id)) %>% 
  ggplot(aes(x = level_id, y = sent_len, fill = level_id)) + 
  geom_boxplot() + 
  scale_y_continuous(limits = c(0,200))



```




```{r}
KLC_TTR_vis %>% 
  ggplot(aes(x = Level, y = TTR)) +
  geom_point() +
  geom_path() +
  geom_line() + 
  geom_smooth(method = "lm", formula = y ~ x)
```




##### codes needed for my project from Dan (Thanks!!!)


```{r}
PELIC_ans %>% 
  mutate(tokens = tokens %>% 
           str_remove_all("\\['|'\\]|\\s") %>% 
           str_split("','")) %>% 
  unnest(tokens)
```

```{r}
tibble(col1 = list(c('I', 'I', 'PRP'),
                   c('met', 'meet', 'VBD'),
                   c('my', 'my', 'PRP$'))) %>%
  mutate(Word = map(col1, 1),
         Lemma = map(col1, 2),
         POSTag = map(col1, 3)) %>% 
  unnest(Word:POSTag)
```

```{r}
KLC_clean$Morphemes[1] %>% 
  str_split("\\s(?!\\+)") %>% 
  flatten_chr() %>%
  str_split(" \\+") %>% 
  head(3)
```




```{r, error=TRUE}
PELIC_ans1 %>% 
  unnest_tokens(word, text) %>% 
  left_join(PELIC_ans %>% select(), by="")

# 이렇게하면 unnest하느라 없어졌던 열들을 다시 갖다 붙일 수 있음!

# %>% mutate(number = str_extract(colname, "regex"))
# 특정 열에서 특정 표현만 추출.
```


overfitting
; 모델이 샘플에 너무 딱 맞으면 전체 population에 대한 대표성을 잃는다.

correlation and regression trees (CART) ; 한가지 해결방법
ensemble method; 다른 해결방법
random forest?
ranger package로 가지고 random forest를 쓸 수 잇음.

overlearning
; 




